\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Project Proposal: Online Notes App (JustNote)\\
{\footnotesize \textsuperscript{}CSE-0318 Summer 2021 }
%\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{Saber Ahmed}
\IEEEauthorblockA{\textit{Department of Computer Science and Engineering} \\
\textit{State University of Bangladesh (SUB)}\\
Dhaka, Bangladesh \\
dev.saberahmed@gmail.com} 
%\and
%\IEEEauthorblockN{Khan Md. Hasib}
%\IEEEauthorblockA{\textit{Department of Computer Science and Engineering} \\
%\textit{State University of Bangladesh (SUB)}\\
%Dhaka, Bangladesh  \\
%hasib@sub.edu.bd}
}

\maketitle

\begin{abstract}

JustNote online app allows users to create notes, which will be text.\\


\end{abstract}


\begin{IEEEkeywords}
HTML, CSS, Bootstrap, PHP, MySQL, AJAX
\end{IEEEkeywords}

\section{Introduction}
Write anything to make it as a note. User can make as many as note user wants.\\ Every user will have individual account for saving their notes. There will be landing page, my note page \& profile page. 

\section{Literature Review}

Evernote is an app designed for note taking, organizing, task management, and archiving. It is developed by the Evernote Corporation, headquartered in Redwood City, California.\\ The app allows users to create notes, which can be text, drawings, photographs, audio, or saved web content. Notes are stored in notebooks and can be tagged, annotated, edited, searched, given attachments, and exported.

\section{Proposed Methodology}

Landing page will contain Signup, Login, Remember me \& Forgot password options. After successful login, user will land in My Note page contain All Notes, Edit Notes, Delete Notes options. On the Profile page, user can Update email and password.




\section*{Acknowledgment}

I would like to thank my honourable\textbf{ Khan Md. Hasib Sir} for his time, generosity and critical insights into this project.




\begin{thebibliography}{00}
\bibitem{b1} Schepman, A., Rodway, P., Beattie, C., \& Lambert, J. (2012). An observational study of undergraduate students’ adoption of (mobile) note-taking software. Computers in human behavior, 28(2), 308-317.
\bibitem{b2} Walsh, E., \& Cho, I. (2013). Using Evernote as an electronic lab notebook in a translational science laboratory. Journal of laboratory automation, 18(3), 229-234.

\end{thebibliography}
\vspace{12pt}

\end{document}
